---
title: "LMwithPrediction"
author: "Daniel Jones"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is the linear model with prediction problem.  
Predict strength scores using the data from the following website.  

```{r}
data <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```  

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(ggplot)
require(rgl)
require(knitr)
```


### Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
new=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,new,interval = "prediction")
```
```{r}
plot(SIMS~GRIP,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

Model 1 fit, the adjusted r-squared is 0.467. About 47% of the variability in SIMS can be explained by the variability in ARM. The predicted score for SIMS is 0.71  The 95% confidence interval is from -1.726209 to 3.138977.

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict.lm(model.2,new,interval = "prediction")
```

model 2 fit, the adjusted r-squared is .4053 About 41% of the variability in SIMS can be explained by the variability in GRIP. The predicted score in SIMS is -0.54   The 95% confidence interval is from -3.167561 to 2.035652

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict.lm(model.3,new,interval = "prediction")
```

model 3 fit, the adjusted r-squared is 0.5350 About 54% of the variability in SIMS can be explained by the variability in both ARM and GRIP. The predicted score in SIMS is .15 The 95% confidence interval is from -2.132373 to 2.431668

```{r}
anova(model.1,model.3)
```
null hypothesis: there is no difference in the models    
alternative hypothesis: there is a difference in the models    
The p-value is .00000499

Conclusion:   
We reject the null hypothesis because the p-value is less than .05


